Impact of interaction network structure on community-level plant reproductive success

### 2018-12-05 paper_round2.Rmd
finish comenting in this.

f2$tot.visits.sc<-((f2$tot.visits-min(f2$tot.visits))/(max(f2$tot.visits)-min(f2$tot.visits)))  #scale number of visits

@@

library(bbmle)
AICtab(m1, m2, m3) #best model is m2
#yes, but m3 is 0.6 AIC away... which is nothing...

@@

#scale seed number
head(s2)
s2$mean.seedn.sc<-((s2$mean.seedn-min(s2$mean.seedn))/(max(s2$mean.seedn)-min(s2$mean.seedn))) 
#This scaling is not working like that. 1) scale() will do that for you. 2) you need to scale each plant in turn.
library(dplyr)
s2 %>% 
  group_by(Plant.sp) %>%

@@

 m1.seed<-glmmTMB(mean.seedn.sc ~  norm_degree + tot.visits.sc +  (1|Site_ID) + (1|Site_ID), family="poisson", data=s2)
 summary(m1.seed)
#Ojo, AIC changes if the second (1|Site_ID) is removed.
 m2.seed<-glmmTMB(mean.seedn.sc ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="poisson", data=s2)
 summary(m2.seed)

m3.seed<-glmmTMB(mean.seedn.sc ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="poisson", data=s2)
summary(m3.seed)

library(bbmle)
AICtab(m1.seed, m2.seed, m3.seed)

#test for problems in residuals
res<-simulateResiduals(m2.seed)
plot(res, rank = TRUE)

@@

#try removing Cistus ladanifer with very large values 
#But this do not makes much sense, if they are scaled by species...

@@

library(bbmle)
AICtab(m1.seedw, m2.seedw, m3.seedw)

@@

### Network-level
#### FRUITSET
We find that at the level of the whole communty, differences in average fruit set are driven particularly by the diversity of pollinator species. In this sense, we find that communities with greater pollinator diversity have lower values of fruit set but consistent higher values of other function aspects measured: seed number per fruit, fruit and seed weight. In contrast, we found that metrics accounting for the structure of interactions between plants and pollinators had little or no effect for functioning.

@@

library(bbmle)
AICtab(m1.fr, m2.fr, m3.fr)

@@

#seed number

@@

@@

f4$fruit.prop<-f4$mean.fruitset/f4$fruit.max
f5<-subset(f4, f4$fruit.prop>0.5)
f5$no_rows<-rep(1, nrow(f5))

#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
f6<- aggregate(no_rows ~ Site_ID, f5, length)

@@

library(bbmle)
AICtab(m1.eq, m2.eq, m3.eq)

@@

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
#First attempt to load the data, etc...

>>>>

f2$tot.visits.sc<-((f2$tot.visits-min(f2$tot.visits))/(max(f2$tot.visits)-min(f2$tot.visits)))  #scale number of visits
head(f2)
#why this is done? visits whould be all in the same scale already? 
#If it is to correct for different atractiveness, you should scale as below (by plant)
#If it is to scale the predictors and make estimates comparable, you should do that to all predictors.

@@

library(bbmle)
AICtab(m1, m2, m3) #best model is m2
#yes, but m3 is 0.6 AIC away... which is nothing... and m1 with just one random is almost equal too!

@@

#scale seed number
head(s2)
s2$mean.seedn.sc<-((s2$mean.seedn-min(s2$mean.seedn))/(max(s2$mean.seedn)-min(s2$mean.seedn))) 
#This scaling is not working like that. 1) scale() will do that for you. 2) you need to scale each plant in turn.
library(dplyr)
s3 <- s2 %>% 
  group_by(Plant.sp) %>% 
  mutate(mean.seedn.sc = scale(mean.seedn, center = T, scale = T))
dim(s2)
dim(s3)
head(s3)

#FOR TESTING PUROSES I overwrite s2
s2 <- s3

@@

 m1.seed<-glmmTMB(mean.seedn.sc ~  norm_degree + tot.visits.sc +  (1|Site_ID) + (1|Site_ID), family="gaussian", data=s2)
 summary(m1.seed)
#Ojo, AIC changes if the second (1|Site_ID) is removed.
 m2.seed<-glmmTMB(mean.seedn.sc ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="gaussian", data=s2)
 summary(m2.seed)

m3.seed<-glmmTMB(mean.seedn.sc ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="gaussian", data=s2)
summary(m3.seed)

library(bbmle)
AICtab(m1.seed, m2.seed, m3.seed) #2 is better, but all of them are pretty bad...

#test for problems in residuals
res<-simulateResiduals(m2.seed)
plot(res, rank = TRUE)
#residuals good with scaled and gaussian

@@

#try removing Cistus ladanifer with very large values 
#But this do not makes much sense, if they are scaled by species... see above.

@@

library(bbmle)
AICtab(m1.seedw, m2.seedw, m3.seedw) #again, very similar (and bad) models.

@@

```
[IB: I wonder if AIC is what we want here. Why compare models 1 and 2? One option is to present directly m3. Or m1 vs m3 maybe. I don't have a clear idea... skype?]
### Network-level
#### FRUITSET
We find that at the level of the whole communty, differences in average fruit set are driven particularly by the diversity of pollinator species. In this sense, we find that communities with greater pollinator diversity have lower values of fruit set but consistent higher values of other function aspects measured: seed number per fruit, fruit and seed weight. In contrast, we found that metrics accounting for the structure of interactions between plants and pollinators had little or no effect for functioning.

@@

library(bbmle)
AICtab(m1.fr, m2.fr, m3.fr) #m3 is as good!!!
##I hate models... m2 nodf is sig, m3 fc is sig!! WHY!!! colineality issues?

@@

#seed number
#How mean seed number is calculated?? scaled first would be better, right?

@@

#fruit weight
#How mean seed number is calculated?? scaled first would be better, right? At least if fruits vary in orders of magnitude.

@@

f4$fruit.prop<-f4$mean.fruitset/f4$fruit.max
f5<-subset(f4, f4$fruit.prop>0.5)
f5$no_rows<-rep(1, nrow(f5))
head(f5)

#NOTE TO SELF: Here is where we want to subsample 1 to 6 species per site to test the idea of increasing plants, complementarity increase.

#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
f6<- aggregate(no_rows ~ Site_ID, f5, length)
head(f6)

@@

library(bbmle)
AICtab(m1.eq, m2.eq, m3.eq) #m3 as good almost

@@

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
#IB edited this in paper.Rmd
#First attempt to load the data, etc...
